\vspace{-3em} \includegraphics[width=.1\textwidth]{Figures/logo.png} \\ \includegraphics[width=4cm]{Figures/logotext.png} \\

### 2014-10-09 report/article_4.tex
some report and web tweaks

As an example, Figure 3 shows the top 5 best-ranked postcode sectors
in which to invest, according to their 12-month price growth forecast
and historical annualised volatility --- thus combining the empirical
data with theoretical model outputs. These include South London
suburbs of Upper Tooting and Morden, Walthamstow, as well as Brockley,
whose train station within SE4 1 was linked with the London overground network in 2010.\\

>>>>

As an example, Figure 3 shows the top 5 best-ranked postcode sectors
in which to invest, according to their 12-month price growth forecast
and historical annualised volatility --- thus combining the empirical
data with theoretical model outputs. These include South London
suburbs of Upper Tooting and Morden, as well as Walthamstow in East
London, and Brockley,
whose train station within SE4 1 was linked with the London Overground network in 2010.\\
